\documentclass[a4paper, 10pt]{article}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{framed}
\usepackage{array}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{fancyhdr}
\usepackage{titlesec}
\titleformat{\chapter}[hang]
{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter:}{1em}{}


\setlength{\parindent}{0em}
\newcolumntype{L}{>{\arraybackslash}m{10cm}}
\newcolumntype{T}{>{\arraybackslash}m{6cm}}

\begin{document}
\pagestyle{fancy}
\fancyhead[HR]{STAT-4330 \\ Homework 1 }
\fancyhead[HL]{Frank Ma}

\section{STAT 4330 Fall 2024 Homework 1 Due August 27}

1. What year are you in?  \\

I am a sophomore.   \\

2. Do you have a copy of the textbook? Did you download it from the library?  \\

Yes I have downloaded a copy of the textbook from Penn Libraries.  \\

3. What is your major or concentration?  \\
 
I am intending to concentrate in Finance and Statistics in Wharton, and I am completing an uncoordinated dual degree in CIS.   \\

4. What is your math background? Please list the classes you have taken.  \\

I have taken two semesters of math so far, MATH 1410 and MATH 2600 (2600 taken in replacement of 2400.\\

5. When and with whom did you take STAT 4300? If you did not take STAT 4300 please let me know the equivalent level probability class that you have taken.\\

I took STAT 4300 with Professor Jason Altschuler. \\

6. When and with whom did you take MATH 2400? If you did not take MATH 2400 please let me know the equivalent level linear algebra class you have taken.\\

I took MATH 2600 with Professor Herman Gluck.  \\

7. What statistics classes have you taken? \\

I previously took STAT 1010 and I am currently taken STAT 4310 concurrently with STAT 4330.  \\

8. Do you have any concerns about this class that you wish to ask me about?  \\

None so far!  \\

9. Name one hobby or interest that you are most interested in. \\

I like to stay active (running / swim / gym). 



\end{document}
